---
title: "Homework 2"
subtitle: "Submission 3"
author: "Conor Mulligan"
format:
  pdf:
    output-file: "mulligan-c-hwk2-3"
    output-ext:  "pdf"
    header-includes:
      - \usepackage{float}
      - \floatplacement{table}{H}
---

This is my third submission of homework 2.

[Link to Github](https://github.com/cmulliga/homework-2)

```{r}
#| include: false

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, readr, readxl, hrbrthemes, fixest,
               scales, gganimate, gapminder, gifski, png, tufte, plotly, OECD,
               ggrepel, survey, foreign, devtools, pdftools, kableExtra, modelsummary,
               kableExtra)
```



```{r}
#| include: false
#| eval: true
 
load("/Users/ctmul/Emory_Files/ECON_470-1/homework-2/hwk2_workspace.Rdata")
```


My answers to the homework questions are below. Analysis is done in a separate R workspace.

\newpage
# Summarize the Data

\vspace{.2in}
\noindent 1. How many hospitals filed more than one report in the same year? Show your answer as a line graph of the number of hospitals over time.<br>

```{r} 
#| echo: false
#| fig-cap: Count of Hospitals with more than one Report over Time
  fig.hospital.reports

```

\newpage
\noindent 2. After removing/combining multiple reports, how many unique hospital IDs (Medicare provider numbers) exist in the data? <br>

Looking in the data, we are able to see that there are `r unique.count` hospital IDs.


\newpage
\noindent 3. What is the distribution of total charges (tot_charges in the data) in each year? Show your results with a “violin” plot, with charges on the y-axis and years on the x-axis. .<br>


```{r} 
#| echo: false
#| warning: false

fig.total.charges

```


\newpage
\noindent 4. What is the distribution of estimated prices in each year? Again present your results with a violin plot, and recall our formula for estimating prices from class. Be sure to do something about outliers and/or negative prices in the data.


```{r}
#| echo: false
#| warning: false

fig.prices

``` 


\newpage
# Estimate ATEs

\vspace{.2in}
\noindent 5. Calculate the average price among penalized versus non-penalized hospitals.<br>

The average price after calculating between the two groups is presented in a table below where True is penalized hospitals and False is non penalized hospitals.

```{r}
#| echo: false
#| tbl-cap: Average Price of Penalized vs. Non-Penalized Hospitals
#| warning: false

options(knitr.kable.NA = 0)
knitr::kable(table.price, 
             col.names=c("Penalty","Average Price"),
             format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down"))
```

\newpage

\noindent 6. Split hospitals into quartiles based on bed size. To do this, create 4 new indicator variables, where each variable is set to 1 if the hospital’s bed size falls into the relevant quartile. Provide a table of the average price among treated/control groups for each quartile.<br>

My best attempt at the table is below. As with number 5, false is non-penalized mean price for hospitals and true is penalized mean price for hospitals by quartile. 

```{r}
#| echo: false
#| label: Quartile Table
#| tbl-cap: Prices by Bed Size Quartiles and Penalty
#| warning: false

options(knitr.kable.NA = 0)
knitr::kable(table.quartiles, 
             col.names=c("Penalty","Q1","Q2","Q3",
                         "Q4"),
             format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down"))

```


\newpage
\noindent 7. Find the average treatment effect using each of the following estimators, and present your results in a single table.

For the final submission, I was able to get all estimators working properly. However, I was unable to get row names to properly display for the data shown. The first is Mahalanobis, the second is Propensity Score, and the third is Inverse Matching. Regardless of these troubles, I created the table below.

```{r}
#| echo: false
#| label: ATE table
#| tbl-cap: Estimated ATEs
#| warning: false

options(knitr.kable.NA = 0)
knitr::kable(table.ates, 
             col.names=c("Estimated ATEs"),
             format.args=list(big.mark=","), booktabs = TRUE) %>%
             kable_styling(latex_options=c("scale_down"))
```

Below is the results for the regression, which I could not properly include in the table above.

```{r}
#| echo: false
#| warning: false

summary(reg)

```

\newpage
# Summary Questions


\vspace{.2in}
\noindent 8. With these different treatment effect estimators, are the results similar, identical, very different?<br>

The estimators appear to be identical to each other, with all of them being 193.8 after estimating based on quartiles for bed size.

\newpage
\noindent 9. Do you think you’ve estimated a causal effect of the penalty? Why or why not? (just a couple of sentences)<br>

I think that it is not possible to say that a causal effect was estimated. We might be able to say there is a correlation, but much more analysis based on more data and studies would need to be done to say for certain that the penalty exactly causes an effect.

\newpage
\noindent 10. Briefly describe your experience working with these data (just a few sentences). Tell me one thing you learned and one thing that really aggravated you.<br>

I could not get some of the data to cooperate as I wanted. The regression analysis was able to run properly this time, but I could not properly include the results in one table alongside the other ATEs. Other than that, I tried to improve the clarity of my graphs and the readability of my overally final document, which I think I mostly succeeded in doing.